---
title: "Organize Photos"
author: "Sam Struthers"
date: "8/12/2026"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
`%nin%` = Negate(`%in%`)
library(tidyverse)
library(animation)
library(gganimate)
library(dygraphs)
library(lubridate)
library(xts)
library(exifr)
library(imputeTS)
library(png)
library(grid)
library(ggthemes)
library(patchwork)
library(here)
```

# Basic task:

Organize all site photos into individual site folders in the Timelapse OneDrive Folder (Contact Sam Struthers for access)

## Setup

- Symlink timelapse folder to PSN root directory
- Create two local folders in the timelapse folder: "to_be_compiled" and "zip_dump"

## Running the Script

- Grab the SD card from the camera and copy all the files to a folder in the "to_be_compiled" folder.
  - The folder name should include the site name and the date range of the photos (e.g., "archery_20260301_20260331").
    - Double check that the site name is spelled correctly and matches one of the following: bellvue, tamasag, legacy, timberline, prospect, riverbend, boxelder, archery, riverbluffs, rist, elc. If the site name is not spelled correctly or does not match one of these names, the script will throw an error.
  - **IMPORTANT: Make sure that the camera was recording the correct datetimes, If it wasn't, we cannot use this script to compile the photos.**
- Source/Run the compile_files function
- Run the function over the folder paths as needed.
  - This can take \~ 5 min per site per month's worth of photos
- Copy the zip files in zip_dump to the ROSS field harddrive
- Delete/Clear out your trash as you go along :)

## Get all the names

```{r}
# select site


compile_files <- function(folder_name, compile_file_path = "timelapse_data/2026_compiled/"){
site <- str_extract(folder_name, "bellvue|tamasag|legacy|timberline|prospect|riverbend|boxelder|archery|riverbluffs|rist|elc")
if (is.na(site)) {
  stop(paste0("Error: Could not extract a valid site name from '", folder_name, 
              "'. Please check your folder spelling!"))
}

if (site == "rist" |site == "tamasag" ) {
  site <- "bellvue"
}
if (site == "prospect") {
  site <- "cottonwood"
}
if (site == "timberline") {
  site <- "elc"
}
if (site == "legacy") {
  site <- "salyer"
}

photo_files <- list.files(path = folder_name, full.names = TRUE, recursive = TRUE)

year <- str_extract(compile_file_path, "\\d{4}")
year_check <- grepl(pattern = year, x = folder_name)
if(!year_check){
  stop(paste0("Folder name does not contain the year ", year))
}  

# Ensure target directory exists
dest_path <- paste0(compile_file_path, site, "/")
if(!dir.exists(dest_path)){
  dir.create(dest_path, recursive = TRUE)
}
#zip the original folder first
extract_folder_name <- basename(folder_name)

folder_name_zip <- here("timelapse/zip_dump",paste0(extract_folder_name, ".zip"))
zip(zipfile = folder_name_zip, files = folder_name)

# Get files already in folder to avoid overwriting/re-processing
compiled_folder_files <- list.files(path = dest_path, full.names = TRUE)

print(paste0("Compiling ", folder_name))

photo_renamer <- function(file) {
  # Grab dt from file
  dt <- read_exif(path = file, tags = c("DateTimeOriginal")) %>%
    pull(DateTimeOriginal) %>%
    parse_date_time("YmdHMS", tz="MST") %>%
    format("%Y%m%d_%H%M")
  
  # Create the target file path
  new_file_name <- paste0(dest_path, dt, '.JPG')
  
  # Check if a file with this exact timestamp already exists in the destination
  if (new_file_name %in% compiled_folder_files || file.exists(new_file_name)) {
    # Delete the duplicate source file so it doesn't get left behind
    file.remove(file)
    print(paste0("Skipped & deleted duplicate source file for timestamp: ", dt))
    
  } else {
    # If it doesn't exist, move and rename it
    success <- file.rename(from = file, to = new_file_name)  
    
    if(success) {
      print(paste0("Moved & Renamed: ", basename(file), " -> ", basename(new_file_name)))
      # Dynamically add the new file to our tracking vector so subsequent loop items catch it
      compiled_folder_files <<- c(compiled_folder_files, new_file_name)
    } else {
      warning(paste0("Failed to move: ", file))
    }
  }
}

# Process the files
walk(photo_files, photo_renamer)

#delete the folder after moving all files
fs::dir_delete(folder_name)
print(paste0("Finished ", folder_name))

}
```

# Compiling Files

Couple of examples here:

## Single Folder

```{r}
working_folder <- "timelapse/to_be_compiled/riverbluffs_20260330_20260430/"
compile_files(folder_name = working_folder)
```

## Whole to be compiled folder

```{r}
folders <- list.files(path = "timelapse/to_be_compiled/", full.names = TRUE)

walk(folders, compile_files)
```

## Subset of the folders for a specific site and year

```{r}
#Subet of folders for a specific site and year
folders <- list.files(path = "timelapse/to_be_compiled/", full.names = TRUE)%>%
  # include files that do not have WRONGDATES in the name
  str_subset("riverbend", negate = FALSE)%>%
  str_subset("2025", negate = FALSE)
#copy all the files to the compiled folder
 walk(folders, compile_files)
```

# Plots to view timelapse coverage

Not necessary to run this but you can if you want to make sure the files you uploaded were saved correctly

```{r}
# read in all files names and then break into site and date time by parsing the file and folder name
all_files <- map(c("timelapse_data/2023_compiled", "timelapse_data/2024_compiled", "timelapse_data/2025_compiled", "timelapse_data/2026_compiled"), ~list.files(path = .x, full.names = TRUE, recursive = TRUE))%>%
  map_df(~{
    site <- str_extract(.x, "tamasag|legacy|timberline|prospect|boxelder|archery|riverbluffs|rist|elc")
    date <- str_extract(.x, "\\d{8}_\\d{4}")
    tibble(site = site, date = date, photo = 1)
  })%>%
  mutate(date = parse_date_time(date, "Ymd_HM"))%>%
  ross.wq.tools::fix_site_names()%>%
  mutate(site = ifelse(site== "rist", "bellvue", site))

# plot the number of photos per day facet by site
all_files%>%
  #filter(site == "archery")%>%
  ggplot(aes(x = date, y = photo))+
  geom_point()+
  facet_wrap(~site)+
  theme_bw()+
  #theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(x = "Date", y = "Number of Photos", title = "Number of Photos per Day")
```
