---
title: "Step 1 — Reconcile Hours & Preview Totals"
author: "ROSSyndicate - Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

# What this does

Run this **before** you touch `pwqn_budget_reporting.xlsx`. It compares the
$ amount Symphony billed for each person (entered in `00_config.R`) against
the hours already logged in the `staff_timeclock` sheet, split across PWQN
and UCLP. Use it to sanity-check your xlsx entries, then re-run after
updating the xlsx to confirm everything reconciles before generating reports.

# User inputs required

-   Edit `month_select` / `year_select` and the Symphony $ amounts below
-   Once a year, update the `hourly_rates` xlsx with the new rates for each person (see `00_config.R`)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
source(here::here("operations/reporting/budget/00_config.R"))
###### ------ Month/Year SELECTOR ------ ######
month_select <- 7
year_select  <- 2026
###### ------ SYMPHONY 53-ACCOUNT $ AMOUNTS ------ ######
#    Paste in the $ billed per person (whole project, both PWQN + UCLP combined,
#    since they share one job code) from Symphony each month.
hours_billed_raw <- tibble::tribble(
  ~person,        ~monthly_amount,
  "STRUTHERS",    0,
  "DE LA TORRE",  0,
  "WILLI",        0,
  "ROUIN",        0,
  "DUNCAN",       0
)

###### ------ NON-PERSONNEL (equipment/travel) COSTS, per project------ ######
#    These usually come straight off the equipment_charges / travel sheets in
#    the xlsx (see budget_functions::load_equipment()/load_travel()), but if
#    you need to hand-override a project's totals for the Symphony 53-account
#    reconciliation step, do it here.
# (left NULL by default -- 01_check_hours.Rmd will pull these live from the xlsx.
#  Only set this if you need to override.)
non_personnel_override <- NULL
```

```{r load}
hourly_rates <- load_hourly_rates(rates_file)
timeclock    <- load_timeclock(reporting_xlsx, month_select, year_select)
equipment    <- load_equipment(reporting_xlsx, month_select, year_select)
travel       <- load_travel(reporting_xlsx, month_select, year_select)

reconciled <- reconcile_hours_and_cost(timeclock, hourly_rates, hours_billed_raw)
```

## 1. Hours: logged (staff_timeclock) vs. implied by $ billed

`remaining_hours` should be close to 0. Positive means added
more hours than should exist based on Symphony Data; negative means
you've added more hours than were billed.
Update the `staff_timeclock` sheet in `pwqn_budget_reporting.xlsx` until this table reconciles.

```{r hours-check}
reconciled$hours_check
```

## 2. Dollars: logged (staff hours x rate) vs. Symphony $ billed

```{r cost-check}
reconciled$cost_check
sum(reconciled$cost_check$remaining_amount) #Should be close to 0, wiggle room <5 $ is okay
```

## 3. Final totals per project (personnel + equipment + travel + IDC)

These are the numbers to copy into the expenditure tracker once the two
tables above reconcile.

```{r final-totals}
final_totals <- calc_final_totals(timeclock, hourly_rates, equipment, travel, idc_rate)%>%
  #make a new row which is the totals for each column
  bind_rows(summarise(., across(where(is.numeric), sum, na.rm = TRUE )))%>%
  #add a new column to the totals row to identify it as totals
  mutate(project = if_else(is.na(project), "TOTAL", project))

final_totals # Double check the totals against the Symphony values and Invoicing sheet
```


**Next step:**  update `pwqn_budget_reporting.xlsx` as needed until the tables above look right, re-run this file to confirm, then
move on to `02_prep_charges_gen_report.Rmd` for each project.
