---
title: "Sensor & Sonde Asset Management"
subtitle: "2026 Sensor Tracking — Deployment Status"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
author: "ROSSyndicate - Field Manager"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(stringr)
library(DT)
library(plotly)
library(ggplot2)
library(here)
library(openxlsx)
library(tidyverse)


# ---- Path to workbook ----
# Update this path as needed
xlsx_path <- here("data/raw/management/equipment_tracking/2026_sensor_tracking.xlsx")

# ---- Update the Workbook based on field notes & cal reports ----

#Load field notes 
source("src/load_mWater_notes.R")
all_notes_cleaned <- load_mWater_notes()
source("src/update_station_info.R")
# This will update the workbook's `station_info` tab with the most recent sonde SNs and vulink info based on field notes
update_station_info(field_notes = all_notes_cleaned,
                    xlsx_path)
source("src/update_sensor_current_locations.R")
# This will update the workbook's `sensor_cur_loc` tab with the most recent sensor locations based on calibration reports and field notes
update_sensor_current_locations(field_notes = all_notes_cleaned,
                                xlsx_path)


ownership   <- read_excel(xlsx_path, sheet = "ownership")
sensor_loc  <- read_excel(xlsx_path, sheet = "sensor_cur_loc")
station_info <- read_excel(xlsx_path, sheet = "station_info")
```

```{r prep}
# ------------------------------------------------------------------
# SONDES
# Sondes are identified as any "Equipment" entry containing "AT"
# (AT500 / AT600 / AT700 / AT800). Each such row in `ownership` is
# one physical sonde
# Deployment status comes from `station_info$current_sonde_sn`,
# which lists the SN currently installed at each site.
# ------------------------------------------------------------------

sondes_owned <- ownership %>%
  filter(is.na(archive))%>%
  filter(str_detect(Equipment, "AT")) %>%
  mutate(SN = as.character(SN)) %>%
  select(Owner, Equipment, SN, date_acquired, notes, lent)

deployed_sonde_sns <- station_info %>%
  filter(!is.na(current_sonde_sn)) %>%
  mutate(current_sonde_sn = as.character(current_sonde_sn)) %>%
  pull(current_sonde_sn)

sondes_owned <- sondes_owned %>%
  mutate(status = case_when(
    !is.na(lent) ~ "Lent",
    SN %in% deployed_sonde_sns ~ "Deployed",
    TRUE ~ "Available"
  )) %>%
  select(-lent)

sonde_summary <- sondes_owned %>%
  count(Equipment, status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0) %>%
  mutate(Total = rowSums(pick(any_of(c("Deployed", "Lent", "Available"))), na.rm = TRUE)) %>%
  arrange(desc(Total))

sonde_totals <- sondes_owned %>%
  count(status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0)

# ------------------------------------------------------------------
# VULINKS
# Vulinks are identified as "Equipment" == "vulink" in `ownership`.
# Deployment status comes from `station_info$current_vulink_sn`,
# which lists the SN currently installed at each site.
# ------------------------------------------------------------------

vulinks_owned <- ownership %>%
  filter(is.na(archive))%>%
  filter(str_to_lower(Equipment) == "vulink") %>%
  mutate(SN = as.character(SN)) %>%
  select(Owner, Equipment, SN, date_acquired, notes, lent)

deployed_vulink_sns <- station_info %>%
  filter(!is.na(current_vulink_sn)) %>%
  mutate(current_vulink_sn = as.character(current_vulink_sn)) %>%
  pull(current_vulink_sn)

vulinks_owned <- vulinks_owned %>%
  mutate(status = case_when(
    !is.na(lent) ~ "Lent",
    SN %in% deployed_vulink_sns ~ "Deployed",
    TRUE ~ "Available"
  )) %>%
  select(-lent)

vulink_summary <- vulinks_owned %>%
  count(Equipment, status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0) %>%
  mutate(Total = rowSums(pick(any_of(c("Deployed", "Lent", "Available"))), na.rm = TRUE)) %>%
  arrange(desc(Total))

vulink_totals <- vulinks_owned %>%
  count(status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0)

# ------------------------------------------------------------------
# SENSORS
# `sensor_cur_loc` holds one row per individual sensor  with
# its current deployed location. This is generated from calibration reports and 
#`src/update_sensor_current_locations.R` script.
#`site == "Lab"` means it's not deployed (i.e. available);
# any other site value means it is deployed.
# ------------------------------------------------------------------

clean_sensor_name <- function(x) {
  x <- str_trim(x)
  case_when(
    str_to_lower(x) %in% c("turb") ~ "Turbidity",
    str_to_lower(x) %in% c("ph") ~ "pH/ORP",
    str_to_lower(x) %in% c("cond") ~ "Conductivity",
    str_to_lower(x) %in% c("do","rdo") ~ "RDO (DO)",
    str_to_lower(x) %in% c("rdo_blue") ~ "RDO Blue (DO)",
    str_to_lower(x) %in% c("chla") ~ "Chlorophyll-a",
    str_to_lower(x) %in% c("fdom") ~ "FDOM",
    TRUE ~ x
  )
}

sensors <- sensor_loc %>%
  filter(!is.na(sensor)) %>%
  mutate(
    sensor_type = clean_sensor_name(sensor),
    status = if_else(str_to_lower(site) == "lab", "Available", if_else(str_to_lower(site) == "lent out", "Lent", "Deployed"))
  )

sensor_summary <- sensors %>%
  count(sensor_type, status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0) %>%
  mutate(Total = rowSums(pick(any_of(c("Deployed", "Lent", "Available"))), na.rm = TRUE))%>%
  arrange(desc(Total))

sensor_totals <- sensors %>%
  count(status) %>%
  pivot_wider(names_from = status, values_from = n, values_fill = 0)
```

## Overview

This report summarizes current deployment status for **sondes** (multi-parameter
housings, identified as `Equipment` values containing "AT" — AT500/600/700/800),
**vulinks** (identified as `Equipment == "vulink"`), and **individual sensors**
(turbidity, pH, conductivity, DO, chlorophyll-a, FDOM, etc.) based on the
`ownership`, `sensor_cur_loc`, and `station_info` tabs.

```{r headline-numbers}
`%||%` <- function(a, b) if (length(a) == 0 || is.na(a)) b else a

sonde_deployed  <- sonde_totals$Deployed %||% 0
sonde_available <- sonde_totals$Available %||% 0
sonde_lent      <- sonde_totals$Lent %||% 0
vulink_deployed  <- vulink_totals$Deployed %||% 0
vulink_available <- vulink_totals$Available %||% 0
vulink_lent      <- vulink_totals$Lent %||% 0
sensor_deployed  <- sensor_totals$Deployed %||% 0
sensor_available <- sensor_totals$Available %||% 0
sensor_lent      <- sensor_totals$Lent %||% 0

stat_card <- function(value, label, bg) {
  htmltools::tags$div(
    style = paste0("flex:1; min-width:160px; background:", bg, "; color:white; padding:20px; border-radius:8px; text-align:center;"),
    htmltools::tags$h3(value, style="margin:0; font-size:2.2em;"),
    htmltools::tags$p(label, style="margin:0;")
  )
}

stat_row <- function(...) {
  htmltools::tags$div(
    style = "display:flex; gap:20px; flex-wrap:wrap; margin-bottom: 20px;",
    ...
  )
}

htmltools::tagList(
  stat_row(
    stat_card(sonde_deployed, "Sondes Deployed", "#2c3e50"),
    stat_card(sonde_lent, "Sondes on Loan", "#f39c12"),
    stat_card(sonde_available, "Sondes Available", "#18bc9c")
  ),
  stat_row(
    stat_card(vulink_deployed, "Vulinks Deployed", "#2c3e50"),
    stat_card(vulink_lent, "Vulinks on Loan", "#f39c12"),
    stat_card(vulink_available, "Vulinks Available", "#18bc9c")
  ),
  stat_row(
    stat_card(sensor_deployed, "Sensors Deployed", "#2c3e50"),
    stat_card(sensor_lent, "Sensors on Loan", "#f39c12"),
    stat_card(sensor_available, "Sensors Available", "#18bc9c")
  )
)
```

---

## Sondes {.tabset}

### Summary Table

```{r sonde-table}
datatable(
  sonde_summary,
  rownames = FALSE,
  options = list(dom = 't', pageLength = 10),
  caption = "Sondes by type: deployed vs. available"
) %>%
  DT::formatStyle('Available', backgroundColor = DT::styleInterval(0, c('white', '#d4f5ec')))
```

### All Sondes (detail)

```{r sonde-detail}
datatable(
  sondes_owned %>% mutate(date_acquired = as.Date(date_acquired))%>% arrange(Equipment, status),
  rownames = FALSE,
  filter = "top",
  options = list(pageLength = 15),
  caption = "Every sonde on record, with owner and current status"
)
```

---

## Vulinks {.tabset}

### Summary Table

```{r vulink-table}
datatable(
  vulink_summary,
  rownames = FALSE,
  options = list(dom = 't', pageLength = 10),
  caption = "Vulinks: deployed vs. available"
) %>%
  DT::formatStyle('Available', backgroundColor = DT::styleInterval(0, c('white', '#d4f5ec')))
```

### All Vulinks (detail)

```{r vulink-detail}
datatable(
  vulinks_owned %>% mutate(date_acquired = as.Date(date_acquired)) %>% arrange(status),
  rownames = FALSE,
  filter = "top",
  options = list(pageLength = 15),
  caption = "Every vulink on record, with owner and current status"
)
```

---

## Sensors {.tabset}

### Summary Table

```{r sensor-table}
datatable(
  sensor_summary,
  rownames = FALSE,
  options = list(dom = 't', pageLength = 10),
  caption = "Sensors by type: deployed vs. available"
) %>%
  DT::formatStyle('Available', backgroundColor = DT::styleInterval(0, c('white', '#d4f5ec')))
```

### Deployed vs Available (chart)

```{r sensor-chart}
sensor_long <- sensors %>% count(sensor_type, status)

p2 <- ggplot(sensor_long, aes(x = reorder(sensor_type, -n), y = n, fill = status,
                               text = paste0(sensor_type, " — ", status, ": ", n))) +
  geom_col(position = "stack") +
  scale_fill_manual(values = c("Deployed" = "#2c3e50", "Lent" = "#f39c12","Available" = "#18bc9c")) +
  labs(x = "Sensor Type", y = "Count", fill = "Status",
       title = "Sensor Inventory by Type") +
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

ggplotly(p2, tooltip = "text")
```


### All Sensors (detail)

```{r sensor-detail}
datatable(
  sensors %>%
    select(sn, sensor_type, owner, site, status, last_calibrated) %>%
    mutate(last_calibrated = as.Date(last_calibrated)) %>%
    arrange(sensor_type, status),
  rownames = FALSE,
  filter = "top",
  options = list(pageLength = 15),
  caption = "Every sensor on record, with owner, current site, and status"
)
```

---

## Notes on methodology
The majority of this data/report is generated automatically from the `ownership`, `sensor_cur_loc`, and `station_info` tabs of the 2026 Sensor Tracking workbook. The `sensor_cur_loc` tab is generated from calibration reports and field notes using the `src/update_sensor_current_locations.R` script, and the `station_info` tab is updated from field notes using the `src/update_station_info.R` script. **You must ensure that the calibration reports and field notes are up to date in order for this report to be accurate.**

- **Archived** units are excluded entirely: any `ownership` row where `archive`
  is filled in is dropped before sonde/vulink counts are built, since those
  units are retired from the active pool.
- **Lent** units are *not* excluded — they're tracked as their own status so
  the pool of active-but-currently-unavailable equipment stays visible:
  - **Sondes/Vulinks**: a row is marked **Lent** if `ownership$lent` is filled
    in (this check happens before deployed/available, so a lent unit is
    reported as Lent even if its SN also appears in `station_info`).
  - **Sensors**: a row is marked **Lent** if `sensor_cur_loc$site` is
    `"lent out"` (also checked before the deployed/available split).
- **Sondes**: identified from the `ownership` tab as any row whose `Equipment`
  value contains "AT" (AT500/AT600/AT700/AT800 sonde bodies). A non-lent,
  non-archived sonde is marked **Deployed** if its serial number appears in
  `station_info$current_sonde_sn`, otherwise **Available**.
- **Vulinks**: identified from the `ownership` tab as any row whose `Equipment`
  value equals "vulink" (case-insensitive). A non-lent, non-archived vulink is
  marked **Deployed** if its serial number appears in
  `station_info$current_vulink_sn`, otherwise **Available**.
- **Sensors**: taken from `sensor_cur_loc`, one row per physical sensor probe.
  A sensor is marked **Available** if its `site` is `"Lab"`, **Lent** if its
  `site` is `"lent out"`, and **Deployed** otherwise. 
- Rows with missing `sensor`/`Equipment` values are excluded from counts.

