---
title: "2022_data-deconfliction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the workflow for deconflicting 2022 Poudre Sonde Network data. This data was collected before our current protocol was produced, and therefore requires a slightly different workflow for performing our auto-QAQC pipeline. Certain factors which necessitate this workflow include:
- Timezone issues throughout multiple datasets
- Inconsistent data formatting across different sources
- Mix of manual datasets (e.g., .csv, .txt, .xlsx) and automated datasets (.htm)
- Duplicate files within the log folder

## 1) Set-up

### 1.1) Package Load
```{r}
# load required packages
package_loader <- function(x) {
  if (x %in% installed.packages()) {
    suppressMessages({
      library(x, character.only = TRUE)
    })
  } else {
    suppressMessages({
      install.packages(x)
      library(x, character.only = TRUE)
    })
  }
}
non_cran_packages <- c("rossyndicate/ross.wq.tools")
invisible(
  lapply(non_cran_packages, function(x) {
    pack_name <- unlist(strsplit(x, "/"))[2] #get package name (no GH username)
    
    if (pack_name %in% installed.packages()) {
      suppressMessages({
        library(pack_name, character.only = TRUE)
      })
    } else {
      suppressMessages({
        devtools::install_github(x)
        library(pack_name, character.only = TRUE)
      })
    }
  })
)
# load all required packages
invisible(
  lapply(c("arrow", "data.table", "httr2", "tidyverse", "lubridate", "zoo", "ggpubr",
           "plotly", "padr", "stats", "RcppRoll", "yaml", "here", "furrr", "ross.wq.tools"),
         package_loader)
)

```

### 1.2) Parallel Compute Configuration
```{r}
# Configure parallel processing
max_workers <- 4  # Maximum number of parallel workers
num_workers <- min(availableCores() - 1, max_workers)
plan(multisession, workers = num_workers)
furrr_ops <- furrr_options(globals = TRUE,
                           packages = c("arrow", "data.table", "httr2", "tidyverse", "lubridate", "zoo",
                                        "padr", "stats", "RcppRoll", "yaml", "here", "ross.wq.tools")
                           )
```

## 2) Credentials, Thresholds, Field Notes

### 2.1) Credentials
```{r}
# Configure your credentials files
mwater_creds_file <- here("creds","creds","mWaterCreds.yml")
mWater_creds <- read_yaml(mwater_creds_file)

# pull field data from mWater API
mWater_data <- load_mWater(creds = mWater_creds)

# grab sensor malfunction records - so auto-QAQC works.
sensor_malfunction_notes <- grab_mWater_malfunction_notes(mWater_api_data = mWater_data) %>%
  mutate(start_DT = with_tz(start_DT, tzone = "UTC"),
         end_DT = with_tz(end_DT, tzone = "UTC"))

```

### 2.2) Thresholds
```{r}
# Read in the threshold data first
sensor_thresholds <- read_yaml(here("data","derived","auto_qaqc_files", "thresholds", "sensor_spec_thresholds.yml"))
season_thresholds <- read_csv(here("data","derived","auto_qaqc_files", "thresholds", "seasonal_thresholds20260304-T175010Z.csv"), show_col_types = FALSE) %>%
  fix_site_names()
```

### 2.3) Directories and Field Notes
```{r}
base_dir <- here("data","raw", "sensor","manual_data_verification","2022_cycle")
meta_folder_path <- here(base_dir, "in_progress","meta")
# Folder with downloaded logs
log_dir <- here("data","raw", "sensor", "log_download", "2022")
decon_log_dir <- here(log_dir, "deconflict_logs")

all_field_notes <- read_parquet(here(meta_folder_path, "field_notes_21-22.parquet")) %>%
  filter(date >= as.Date("2022-01-01"),
         date <= as.Date("2022-12-31")) %>%
  ross.wq.tools::fix_site_names()
```

## 3) Raw Data Ingest & Standardization

### 3.1) Ingest Data

#### 3.1.1) Rist (Bellvue)

- Start: 2022-04-22
- End: 2022-05-24
- Notes: 
  - Sensor “capped” during low flow period. Damaged during peak flows and not re-installed during 2022.
  - Sonde housing destroyed sometime before 2022-05-24

```{r}
# OG timezone in UTC
bellvue_final <- xml2::read_html(here::here(decon_log_dir, "bellvue_all_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log() %>%
  # Sensor pulled 2022-05-30 after sensor housing destroyed
  dplyr::filter(DT_round <= ymd("2022-05-25")) %>%
  # Sensor also capped from 5/6/2022 - 5/9/2022 (flow too low) (timezone in UTC)
  dplyr::filter(!(DT_round >= ymd_hms('2022-05-06 18:00:00') & DT_round <= ymd_hms('2022-05-09 20:30:00'))) %>%
  dplyr::group_by(parameter) %>%
  dplyr::arrange(DT) %>%
  dplyr::mutate(site = "bellvue",
                id = "bellvue",
                name = "bellvue") %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%
  dplyr::ungroup() %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT))

ggplot(data = bellvue_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.2) Legacy (Salyer)

- Start: 2022-04-07
- End: 2022-09-19
- Notes:
    - 2022-05-24: Pulled due to questionable housing integrity
    - 2022-06-01: Redeployed
    - 2022-07-08: Pulled (turbidity & conductivity problems)
    - Between 2022-07-08 & 2022-07-12: turbidity sensor completely breaks; replaced with sensor previously used at archery
    - Between 2022-07-18 & 2022-07-21: back-up sensor stopped working
    - 2022-08-03: Sonde swapped w/ rist
    - 2022-08-03/2022-08-04: Sensor suspended out of water
    - 2022-08-04: Sonde pulled due to low flows
    - 2022-08-25: Redeployed; continued turbidity & ORP issues until end of season
    
```{r}
# Legacy; UTC tz
salyer_1 <- xml2::read_html(here(decon_log_dir, "salyer_1_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log()

salyer_2 <- xml2::read_html(here(decon_log_dir, "salyer_2_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log()

salyer_final <- dplyr::bind_rows(salyer_1, salyer_2) %>% 
  # Remove data ranges where sensor was pulled out of field based on notes (UTC Time)
  dplyr::filter(!((DT_round) >= ('2022-05-24 15:30:00') & (DT_round) < ('2022-06-01 19:30:00')),
              !((DT_round) > ('2022-07-08 20:00:00') & (DT_round) <= ('2022-07-12 16:00:00')),
              !((DT_round) >= ('2022-08-04 15:50:00') & (DT_round) <= ('2022-08-25 22:15:00'))) %>%
  dplyr::mutate(site = "salyer",
                id = "salyer",
                name = "salyer") %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT)) %>%
  dplyr::arrange(DT)

ggplot(data = salyer_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.3) Lincoln (Udall)

- Start: 2022-03-24
- End: 2022-07-22
- Notes:
    - Site ran by in-situ
    - Excel of data sent mid season and not again until end of season, so data is pretty spotty.

```{r}
# OG in UTC even though vu-situ file states -6hr offset from UTC (validated with water temperature)
udall_raw <- readxl::read_excel(here::here(decon_log_dir, "lincoln_all_2022.xlsx"))

udall_final <- udall_raw %>%
  dplyr::mutate(DT_round = lubridate::round_date(DT, "15 minutes")) %>%
  tidyr::pivot_longer(-c("DT", "DT_round"), names_to = "parameter", values_to = "value") %>%
  dplyr::mutate(value = as.numeric(value),
                # Target units
                units = dplyr::case_when(parameter == "Temperature" ~ "C",
                                         parameter == "pH" ~ "pH",
                                         parameter == "ORP" ~ "V",
                                         parameter == "Depth" ~ "m",
                                         parameter == "Specific Conductivity" ~ "µS/cm",
                                         parameter == "DO" ~ "mg/L",
                                         parameter == "Turbidity" ~ "NTU"),
                # Convert values to new units
                value = dplyr::case_when(parameter == "DO" ~ value, # ppm is equivalent to mg/L for dissolved oxygen
                                         parameter == "Depth" ~ value * 0.3048, # feet to meters
                                         parameter == "ORP" ~ value / 1000, # millivolts to volts
                                         TRUE ~ value),
                # Fix site/id/name from lincoln to udall
                site = "udall",
                id = "udall",
                name = "udall"
                ) %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(parameter)) %>%
  dplyr::filter(!is.na(DT)) %>%
  dplyr::arrange(DT)

ggplot(data = udall_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.4) Timberline (Riverbend)

- Start: 2022-04-06
- End: 2022-11-15
- Notes:

```{r}
# Timberline; UTC
riverbend_final <- xml2::read_html(here(decon_log_dir, "riverbend_all_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log() %>%
  dplyr::group_by(parameter) %>%
  dplyr::arrange(DT) %>%
  dplyr::mutate(site = "riverbend",
                id = "riverbend",
                name = "riverbend") %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%
  dplyr::ungroup() %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT))

ggplot(data = riverbend_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.5) Prospect (Cottonwood)

- Start: 2022-04-30
- End: 2022-11-15
- Notes:

```{r}
# Prospect; UTC
cottonwood_final <- xml2::read_html(here(decon_log_dir, "cottonwood_all_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log() %>%
  dplyr::group_by(parameter) %>%
  dplyr::arrange(DT) %>%
  dplyr::mutate(site = "cottonwood",
                id = "cottonwood",
                name = "cottonwood") %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%
  dplyr::ungroup() %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT))
  
ggplot(data = cottonwood_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.6) Boxelder (ELC)

- Start: 2022-04-23
- End: 2022-11-15
- Notes:
    - 2022-05-26: Pulled due to unsuitable site (elc_1_2022.htm & elc_2_2022.htm contains data from this deployment in -6hr UTC offset)
    - 2022-07-27: Re-deployed near boxelder WWTP outfall; continued issues with turbidity and ORP until end of season (elc_3_2022.htm contains data from this deployment in UTC)

```{r}
elc_1 <- xml2::read_html(here(decon_log_dir, "elc_1_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log() %>%
  dplyr::mutate(DT = lubridate::ymd_hms(DT) + lubridate::hours(6))

elc_2 <- xml2::read_html(here(decon_log_dir, "elc_2_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log() %>%
  dplyr::mutate(DT = lubridate::ymd_hms(DT) + lubridate::hours(6))

elc_3 <- xml2::read_html(here(decon_log_dir, "elc_3_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log()

elc_final <- elc_1 %>%
  dplyr::bind_rows(elc_2) %>%
  dplyr::bind_rows(elc_3) %>%
  dplyr::mutate(site = "elc",
                id = "elc",
                name = "elc",
                unit = if_else(parameter == "Temperature", "C", unit)) %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT)) %>%
  dplyr::arrange(DT)

ggplot(data = elc_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

#### 3.1.7) Archery

- Start: 2022-04-06
- End: 2022-11-15
- Notes:
    - Swapped w/ back-up sensor (Fossil Creek) due to early season issues with Chl-a, temp, cond.
    - Between 2022-07-01 & 2022-07-06: Burried
    - 2022-07-14: Unclogged
    - 2022-10-04 & 2022-10-07: Sensor capped

```{r}
#OG data in UTC.
archery_1 <- xml2::read_html(here(decon_log_dir, "archery_1_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log()

archery_2 <- xml2::read_html(here(decon_log_dir, "archery_2_2022.htm")) %>%
  ross.wq.tools::parse_insitu_html_log()

archery_final <- dplyr::bind_rows(archery_1, archery_2) %>% 
  dplyr::filter(!((DT_round) >= ('2022-10-04 21:00:00') & (DT_round) < ('2022-10-07 00:00:00'))) %>%
  dplyr::mutate(site = "archery",
                id = "archery",
                name = "archery") %>%
  dplyr::select(site, id, name, DT, DT_round, parameter, value, units = unit) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(!is.na(DT)) %>%
  dplyr::arrange(DT)

ggplot(data = archery_final) + geom_point(aes(x = DT, y = value)) + facet_wrap(~parameter, scales = "free_y")
```

### 3.2) Standardize Data

#### 3.2.1) Combine Site Data
 
```{r}
all_sites <- bind_rows(bellvue_final, salyer_final, udall_final, riverbend_final, 
                       cottonwood_final, elc_final, archery_final)
```

#### 3.2.2) Depth Mis-calibration Correction

```{r}
# Salyer depth corrections
salyer_depth_corrected <- all_sites %>%
    filter(parameter == "Depth",
           site == "salyer") %>%  
  # UTC to MST conversion to link with field notes
  mutate(DT = with_tz(DT, tzone = "MST")) %>%
  # First correction: 2022-04-06 to 2022-04-12
  mutate(value_p1 = ifelse(DT >= ymd_hms('2022-04-06 06:00:00', tz = 'MST') & DT < ymd_hms('2022-04-12 9:20:00', tz = 'MST'), 
                           value + abs(filter(., DT == ymd_hms('2022-04-12 09:15:00', tz = "MST"))$value 
                                       - filter(., DT == ymd_hms('2022-04-12 16:30:00', tz = "MST"))$value), 
                           value)
         ) %>%
  # Second correction: 2022-07-22 to 2022-07-25
  #timestamp > ymd_hms('2022-07-22 16:45:00') & timestamp < ymd_hms('2022-07-25 21:29:00')
  mutate(value_p2 = ifelse(DT > ymd_hms('2022-07-22 09:45:00', tz = 'MST') & DT < ymd_hms('2022-07-25 14:29:00', tz = 'MST'), 
                           value_p1 + abs(filter(., DT == ymd_hms('2022-07-25 14:15:00', tz = "MST"))$value_p1 
                                          - filter(., DT == ymd_hms('2022-07-25 14:29:00', tz = "MST"))$value_p1), 
                           value_p1)
         ) %>%
  mutate(value = value_p2) %>%
  select(-value_p1, 
         -value_p2) %>%
  # Convert timestamp back to UTC
  mutate(DT = with_tz(DT, tzone = "UTC"))

```

```{r}
# Riverbend depth corrections
# weird mis-calibration
riverbend_depth_corrected <- all_sites %>%
  filter(parameter == "Depth",
         site == "riverbend") %>%
  # UTC to MST conversion to link with field notes
  mutate(DT = with_tz(DT, tzone = "MST")) %>%
  # First correction: 2022-04-06 to 2022-04-07
  mutate(value_p1 = ifelse(DT >= ymd_hms('2022-04-06 07:00:00', tz = 'MST') & DT < ymd_hms('2022-04-07 16:56:00', tz = 'MST'), 
                           value + abs(filter(., DT == ymd_hms('2022-04-07 16:15:00', tz = 'MST'))$value 
                                       - filter(., DT == ymd_hms('2022-04-07 17:15:00', tz = 'MST'))$value), 
                           value)
         ) %>% 
  # purposefully shifted sonde up in housing:
  # Second correction: after 2022-09-14
  mutate(value_p2 = ifelse(DT >= ymd_hms('2022-09-14 13:15:00', tz = 'MST'), 
                           value_p1 + abs(filter(., DT == ymd_hms('2022-09-14 13:00:00', tz = "MST"))$value_p1 
                                          - filter(., DT == ymd_hms('2022-09-14 13:15:00', tz = "MST"))$value_p1),
                           value_p1)
         ) %>%
  mutate(value = value_p2) %>%
  select(-value_p1,
         -value_p2) %>%
  # Convert timestamp back to UTC
  mutate(DT = with_tz(DT, tzone = "UTC"))

```

```{r}
# combine corrected depths with original data
all_sites_corrected <- all_sites %>%
  filter(!(parameter == "Depth" & site == "salyer")) %>%
  filter(!(parameter == "Depth" & site == "riverbend")) %>%
  bind_rows(salyer_depth_corrected, riverbend_depth_corrected) %>%
  arrange(site, DT, parameter)
```

```{r}
# Red indicates the complete corrected depth time series
# Black indicates the original depth mis-calibrations
plotly::ggplotly(ggplot() +
  geom_line(data = all_sites %>% filter(parameter == "Depth" & site %in% c("salyer")), aes(x = DT, y = value), color = "black")+
  geom_line(data = all_sites_corrected %>% filter(parameter == "Depth" & site %in% c("salyer")), aes(x = DT, y = value),linetype = "solid", color = "red"))

plotly::ggplotly(ggplot() +
  geom_line(data = all_sites %>% filter(parameter == "Depth" & site %in% c("riverbend")), aes(x = DT, y = value), color = "black")+
  geom_line(data = all_sites_corrected %>% filter(parameter == "Depth" & site %in% c("riverbend")), aes(x = DT, y = value),linetype = "solid", color = "red"))
```

```{r}
### Check old data with corrected data

old_data <- read_parquet(here('data', 'raw', 'sensor', "manual_data_verification", '2022_cycle', 'ip', 'raw_data', 'raw_data_2022.parquet')) |> 
  group_by(site, parameter)

new_data <- read_parquet(here('data', 'raw', 'sensor', "manual_data_verification", '2022_cycle', 'in_progress', 'raw_data', 'raw_data_2022.parquet')) |> 
  group_by(site, parameter)

# 1. Create a unique grouping ID for both dataframes 
# This ensures our list names match perfectly when we split them
old_data <- old_data %>% mutate(group_id = paste(site, parameter, sep = "_"))
new_data <- new_data %>% mutate(group_id = paste(site, parameter, sep = "_"))

# 2. Split the dataframes into named lists
# The drop = TRUE argument removes empty combinations if a site doesn't have a certain parameter
old_list <- split(old_data, old_data$group_id, drop = TRUE)
new_list <- split(new_data, new_data$group_id, drop = TRUE)

# 3. Identify combinations that exist in BOTH lists to prevent errors
common_groups <- intersect(names(old_list), names(new_list))

# 4. Iterate through the common groups and compare
# purrr::map will apply this comparison function to every site_parameter group
mismatches_list <- map(common_groups, function(grp) {
  
  df_old <- old_list[[grp]]
  df_new <- new_list[[grp]]
  
  df_old %>%
    inner_join(df_new, by = "DT_round", suffix = c("_old", "_new")) %>%
    mutate(
      # The comma has been removed from is.na(mean_old)
      is_diff = !near(mean_old, mean_new) | (is.na(mean_old) != is.na(mean_new))
    ) %>%
    filter(is_diff) %>%
    select(DT_round, site_old, parameter_old, mean_old, mean_new) %>%
    rename(site = site_old, parameter = parameter_old)
  
}) %>% 
  set_names(common_groups)
```

```{r}
# 5. Build a plotly comparison (old vs. new) for each site/parameter combo
comparison_plots <- map(common_groups, function(grp) {

  df_old <- old_list[[grp]] %>%
    ungroup() %>%
    select(DT_round, mean) %>%
    rename(old_data = mean)

  df_new <- new_list[[grp]] %>%
    ungroup() %>%
    select(DT_round, mean) %>%
    rename(new_data = mean)

  plot_data <- full_join(df_old, df_new, by = "DT_round") %>%
    arrange(DT_round)

  plot_ly(plot_data, x = ~DT_round) %>%
    add_lines(y = ~old_data, name = "old_data", line = list(color = "black")) %>%
    add_lines(y = ~new_data, name = "new_data", line = list(color = "red")) %>%
    layout(title = grp,
           xaxis = list(title = "Date"),
           yaxis = list(title = "Value"))

}) %>%
  set_names(common_groups)

# Example: view a single site/parameter comparison
comparison_plots[["archery_Temperature"]]
comparison_plots[["bellvue_Temperature"]]
comparison_plots[["cottonwood_Temperature"]]
comparison_plots[["elc_Temperature"]]
comparison_plots[["riverbend_Temperature"]]
comparison_plots[["salyer_Temperature"]]
comparison_plots[["udall_Temperature"]]
```

```{r}
library(arrow)
library(plotly)
library(tidyverse)

verified_dir <- "~/github/poudre_sonde_network/data/raw/sensor/manual_data_verification/2022_cycle/ip/verified_directory"

verified_files_all <- list.files(verified_dir, pattern = "\\.parquet$", full.names = TRUE)

# Read and combine every verified file into one long data frame
# (DT_join is coerced to character since it's stored as either character or
# datetime depending on the file)
verified_data_all <- map(
  verified_files_all,
  ~ read_parquet(.x) %>% as_tibble() %>% mutate(DT_join = as.character(DT_join))
) %>%
  bind_rows() %>%
  # Prefer the verified/corrected value where available, fall back to raw mean
  mutate(value = coalesce(mean_verified, mean)) %>%
  # Drop points flagged as OMIT in the final decision
  filter(final_status != "OMIT" | is.na(final_status))

# One subplot (stacked, shared x-axis) per parameter, combined by site
site_plots <- verified_data_all %>%
  group_by(site) %>%
  group_split() %>%
  set_names(map_chr(., ~ unique(.x$site))) %>%
  map(function(df) {
    param_plots <- df %>%
      group_by(parameter) %>%
      group_split() %>%
      set_names(map_chr(., ~ unique(.x$parameter))) %>%
      map(function(df_param) {
        units <- unique(df_param$units)[1]
        plot_ly(df_param, x = ~DT_round, y = ~value, type = "scatter", mode = "lines",
                name = unique(df_param$parameter)) %>%
          layout(yaxis = list(title = paste0(unique(df_param$parameter), " (", units, ")")))
      })

    subplot(param_plots, nrows = length(param_plots), shareX = TRUE, titleY = TRUE) %>%
      layout(title = unique(df$site))
  })

# Example: view a single site's combined plot
site_plots[["archery"]]
```

```{r}
# Compare Temperature across all sites on one plot
temp_all_sites <- verified_data_all %>%
  filter(parameter == "Temperature")

plot_ly(temp_all_sites, x = ~DT_round, y = ~value, color = ~site,
        type = "scatter", mode = "lines") %>%
  layout(title = "Temperature by site",
         xaxis = list(title = "Date"),
         yaxis = list(title = paste0("Temperature (", unique(temp_all_sites$units)[1], ")")))
```

```{r}
library(slider)

# Smooth Temperature with a centered 2-hour time-based rolling mean before
# finding each day's peak, to avoid short-lived weather noise (e.g. a brief
# cloud break) masquerading as the diel peak. slide_index is used (rather than
# a fixed n-point window) since sampling interval isn't identical across sites.
temp_smoothed <- verified_data_all %>%
  filter(parameter == "Temperature", !is.na(value)) %>%
  arrange(site, DT_round) %>%
  group_by(site) %>%
  mutate(
    value_smooth = slide_index_dbl(
      value, DT_round,
      ~ mean(.x, na.rm = TRUE),
      .before = lubridate::hours(1), .after = lubridate::hours(1)
    )
  ) %>%
  ungroup()

temp_peaks_smooth <- temp_smoothed %>%
  mutate(date = as.Date(DT_round), hour = lubridate::hour(DT_round) + lubridate::minute(DT_round) / 60) %>%
  group_by(site, date) %>%
  slice_max(value_smooth, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  select(site, date, peak_hour = hour, peak_value = value_smooth)

site_typical_smooth <- temp_peaks_smooth %>%
  group_by(site) %>%
  summarise(median_hour = median(peak_hour), .groups = "drop")
site_typical_smooth

# Find sustained (>= 3 consecutive sampled days) multi-day chunks where the
# smoothed peak hour deviates by more than 1 hour from that site's typical
# (median) peak hour
runs_smooth <- temp_peaks_smooth %>%
  left_join(site_typical_smooth, by = "site") %>%
  arrange(site, date) %>%
  mutate(
    dev = ((peak_hour - median_hour + 12) %% 24) - 12,
    dev_bucket = round(dev)
  ) %>%
  group_by(site) %>%
  mutate(
    gap = as.numeric(date - lag(date)),
    new_run = is.na(gap) | gap > 3 | dev_bucket != lag(dev_bucket),
    run_id = cumsum(new_run)
  ) %>%
  group_by(site, run_id) %>%
  summarise(start = min(date), end = max(date), n_days = n(), mean_dev = mean(dev), .groups = "drop") %>%
  filter(n_days >= 3, abs(mean_dev) > 1) %>%
  arrange(site, start)

runs_smooth
```

```{r}
library(arrow)
library(tidyverse)

verified_dir <- "~/github/poudre_sonde_network/data/raw/sensor/manual_data_verification/2022_cycle/ip/verified_directory"

verified_files_all <- list.files(verified_dir, pattern = "\\.parquet$", full.names = TRUE)

# Parse site/parameter from each filename (format: "{site}-{parameter}_FINAL_...parquet")
# and read each file individually, keeping them separate rather than combining
verified_files_nested <- tibble(file = verified_files_all) %>%
  mutate(
    base = basename(file),
    site = str_extract(base, "^[^-]+"),
    parameter = str_extract(base, "(?<=-).+(?=_FINAL_)"),
    data = map(file, ~ read_parquet(.x) %>% as_tibble())
  ) %>%
  select(site, parameter, file, data)

# Nest into one row per site, each holding a tibble (one row per file/parameter)
# of that site's individual file dataframes
site_nested <- verified_files_nested %>%
  group_by(site) %>%
  nest() %>%
  ungroup()

# Also create one variable per site (e.g. archery_df, bellvue_df, ...) in the
# global environment, each a tibble of parameter/file/data for that site's files
site_nested %>%
  pwalk(function(site, data) {
    assign(paste0(site, "_df"), data, envir = .GlobalEnv)
  })

site_nested
archery_df
```

```{r}
library(plotly)

# Build a plotly line plot (value vs. DT_round) for each individual
# dataframe (i.e. each file: one site/parameter combo)
make_file_plot <- function(df, site, parameter) {
  df <- df %>% mutate(value = coalesce(mean_verified, mean))
  units <- unique(df$units)[1]

  plot_ly(df, x = ~DT_round, y = ~value, type = "scatter", mode = "lines") %>%
    layout(title = paste(site, parameter, sep = " - "),
           xaxis = list(title = "Date"),
           yaxis = list(title = paste0(parameter, " (", units, ")")))
}

# Add a "plot" list-column (one plotly per file) to each site's nested tibble
site_nested <- site_nested %>%
  mutate(data = map2(site, data, function(s, df) {
    df %>% mutate(plot = map2(data, parameter, ~ make_file_plot(.x, s, .y)))
  }))

# Re-create the per-site variables (archery_df, bellvue_df, ...) now that
# each includes the "plot" column
site_nested %>%
  pwalk(function(site, data) {
    assign(paste0(site, "_df"), data, envir = .GlobalEnv)
  })

# Example: view the plot for one file
cottonwood_df$plot[[6]]
```
